Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Adding P parameter for phrase dimension.

\begin{center}
\begin{tabular}{ l r }
  $\mathcal{V} = \left\{w_1,w_2,\ldots,w_{\left\vert\mathcal{V}\right\vert}\right\}$ & the vocabulary \\
  $\mathcal{T} = \left\{t_1,t_2,\ldots,t_{\left\vert\mathcal{T}\right\vert}\right\}$ & the part-of-speech tags \\
  $N = 50$ & the word dimension \\
  $V\in M_{N\times\left\vert\mathcal{V}\right\vert}(\mathbb{R})$ & the word lookup table \\
  $\Ket{w_i}\in\mathcal{V}$ & the ``one-hot" vectors \\
  $V\Ket{w_i}\in\mathbb{R}^N$ & the word vectors \\
  $\Big[\bullet;\bullet\Big]$ & vector concatenation \\
\end{tabular}
\end{center}
\vspace{5mm}

@@

\begin{center}
\begin{tabular}{ l r }
  $W_{combine}\in M_{N\times2N}(\mathbb{R})$ & matrix for combining \\
  $b_{combine}\in \mathbb{R}^N$ & bias for combining \\
  $W_{classify}\in M_{\left\vert\mathcal{T}\right\vert\times N}(\mathbb{R})$ & matrix for tagging \\
  $b_{classify}\in \mathbb{R}^{\left\vert\mathcal{T}\right\vert}$ & bias for tagging \\
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ l r }
  $W_{combine,t}\in M_{N\times2N}(\mathbb{R})$ & matrix for combining tag $t$ \\
  $b_{combine,t}\in \mathbb{R}^N$ & bias for combining tag $t$ \\
  $W_{score}\in M_{1\times N}(\mathbb{R})$ & matrix for scoring tags \\
  $b_{score}\in \mathbb{R}$ & bias for scoring tags \\
\end{tabular}
\end{center}

@@

Early on, we randomly initialized our weight matrices and biases using Torch7's uniform tensor function,
\begin{lstlisting}
torch.rand(m, n)
torch.rand(n)
\end{lstlisting}
which draws from $\mathcal{U}[0, 1)$ however, we discovered guidelines for weight initialization from \hyperlink{http://deeplearning.net/tutorial/mlp.html\#mlp}{deeplearning.net/tutorial/mlp.html\#mlp}, borrowed from Glorot and Bengio (2010), and decided to explore how they impacted our training convergence.

@@

After adopting these new ranges, and initializing our biases to start at zero, our attainable accuracies dramatically increased from the values we presented in our slides, from about $60\%$ to about $80\%$.

>>>>

\begin{center}
\begin{tabular}{ l r }
  $\mathcal{V} = \left\{w_1,w_2,\ldots,w_{\left\vert\mathcal{V}\right\vert}\right\}$ & the vocabulary \\
  $\mathcal{T} = \left\{t_1,t_2,\ldots,t_{\left\vert\mathcal{T}\right\vert}\right\}$ & the part-of-speech tags \\
  $N = 50, P = 50$ & word/phrase dimension \\
  $V\in M_{N\times\left\vert\mathcal{V}\right\vert}(\mathbb{R})$ & the word lookup table \\
  $\Ket{w_i}\in\mathcal{V}$ & the ``one-hot" vectors \\
  $V\Ket{w_i}\in\mathbb{R}^N$ & the word vectors \\
  $\Big[\bullet;\bullet\Big]$ & vector concatenation \\
\end{tabular}
\end{center}
\vspace{5mm}

@@

\begin{center}
\begin{tabular}{ l r }
  $W_{combine}\in M_{P\times(P+N)}(\mathbb{R})$ & matrix for combining \\
  $b_{combine}\in \mathbb{R}^P$ & bias for combining \\
  $W_{classify}\in M_{\left\vert\mathcal{T}\right\vert\times P}(\mathbb{R})$ & matrix for tagging \\
  $b_{classify}\in \mathbb{R}^{\left\vert\mathcal{T}\right\vert}$ & bias for tagging \\
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ l r }
  $W_{combine,t}\in M_{P\times(P+N)}(\mathbb{R})$ & matrix for tag $t$ \\
  $b_{combine,t}\in \mathbb{R}^P$ & bias for tag $t$ \\
  $W_{score}\in M_{1\times P}(\mathbb{R})$ & matrix for scoring \\
  $b_{score}\in \mathbb{R}$ & bias for scoring \\
\end{tabular}
\end{center}

@@

Early on, we randomly initialized our weight matrices and biases using Torch7's uniform tensor function,
\begin{lstlisting}
torch.rand(P, P+N)
torch.rand(P)
\end{lstlisting}
which draws from $\mathcal{U}[0, 1)$ however, we discovered guidelines for weight initialization from \hyperlink{http://deeplearning.net/tutorial/mlp.html\#mlp}{deeplearning.net/tutorial/mlp.html\#mlp}, borrowed from Glorot and Bengio (2010), and decided to explore how they impacted our training convergence.

@@

After adopting these new ranges, and initializing our biases to start at zero, our attainable accuracies dramatically increased from the values we presented in class in our slides, from about $60\%$ to about $80\%$.
